Finite element analysis of multi-dimensional and simplified models for beams

### 2024-04-17 final_seminar/main.tex
presentation

\section{Introduction}
    \begin{frame}{Introduction}
        Beams are fundamental structural elements in engineering. They are used in a wide range of applications, from bridges to buildings.
        \pause

        Simplified models are often used in vibration problems due to their reduced complexity and computational demand. However, the accuracy of these models in practical applications is not always certain.
        \pause

@@

            \textbf{Key Findings:}
            \begin{itemize}
              \item Timoshenko model results closely match those from the two-dimensional model, with most eigenvalues showing less than 3\% deviation, depending on the shape of the beam.
              \item The shape of the beams significantly influences the accuracy of the Timoshenko model.
            \end{itemize}

@@

@@

            Find a real number $\lambda$ and a $x \in V$ with $x \neq 0$ such that
            \begin{eqnarray*}
                b(x,y) = \lambda c(x,y) \ \ \ \ \textrm{ for each } \ y \in V.
            \end{eqnarray*}

>>>>

\section{Introduction}
    \begin{frame}{Introduction}
        Beams are fundamental structural elements in engineering. They are used in a wide range of applications, from bridges to buildings.

        Simplified models are often used in vibration problems due to their reduced complexity and computational demand. However, the accuracy of these models in practical applications is not always certain.

@@

            \textbf{Key Findings:}
            \begin{itemize}
              \item Timoshenko model results closely match those from the two-dimensional model, especially for the first ten eigenvalues.
              \item The shape of the beams significantly influences the accuracy of the Timoshenko model.
            \end{itemize}

@@

        \begin{frame}{Models - Three-dimensional cantilever beam}
            Assume that $\sigma_{3i} = 0$ for $i = 1, 2, 3$; $\partial_3 u_1 = 0$, $\partial_3 u_2 = 0$ ($u_1$ and $u_2$ are functions of $x_1$ and $x_2$), and the strain component $\varepsilon_{33} = 0$. Then using the definition of strain 
            \begin{eqnarray}
                \partial_i u_3 = 0 \quad \textrm{ for } i = 1,2,3 \textrm{ on } \Omega.
            \end{eqnarray}

            It follows that $u_3$ is a constant on $\Omega$ and $u$ is a vector valued function in $R^2$ with two-dimensional stress and strain. The out of plane conditions for strain \eqref{plane_stress_neseccary_condition} falls away and Hooke’s law can be written in a two-dimensional form using the stress components (1.2.16) as $\displaystyle T = \frac{1}{\gamma(1+\nu)}\mathcal{E} + \frac{\nu}{\gamma(1-\nu^2)}\textrm{tr}(\mathcal{E})I.$\\

@@

            Find a real number $\lambda$ and a $x \in V$ with $x \neq 0$ such that
            \begin{eqnarray}
                b(x,y) = \lambda c(x,y) \ \ \ \ \textrm{ for each } \ y \in V.
            \end{eqnarray}
